Next Trippy Structures\thanks{Supported by organization x.}

### 2019-03-11 paper.tex
Add Golynski et al

These operations can be supported in constant time with $o(n)$ extra bits \cite{Jac89,Mun96}, although several techniques exist for compressing bitvectors \cite{Raman:2002:SID:545381.545411,okanohara2007practical}. \marginpar{WTF is wrong with \cite{Golynski2007}?? I cannot find it, paywalls everywhere. Someone (Fari?) cited it before, but I am not going to cite something I cannot read...}

>>>>

These operations can be supported in constant time with $o(n)$ extra bits \cite{Jac89,Mun96}, although several techniques exist for compressing bitvectors \cite{Raman:2002:SID:545381.545411,okanohara2007practical,Golynski2007}.
